Curvature Enhance with Laplacian Operator for Hybrid Quad/Triangle Meshes

### 2013-01-05 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

%% LyX 2.0.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,annual]{acmsiggraph}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amssymb}
\usepackage{graphicx}

@@

% Author and Affiliation (multiple authors).
\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}\\ Cimalab Research Group %
\and Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}\\Cimalab Research Group}
%\and Ton Roosendaal\thanks{e-mail:ton@blender.org}\\ Blender CEO}

% The ``pdfauthor'' command accepts the authors of the work,
% comma-delimited, and adds this information to the PDF metadata.
\pdfauthor{Alexander Pinzon, Eduardo Romero, Ton Roosendaal}

@@

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel method for modeling polygonal mesh using
curvature enhancing. This method use our extension of Laplace Beltrami
operator for hybrid quad/triangle meshes to enhance global curvature
in the model. This work present a novel applications of curvature
enhancement in sculpting and modeling with subdivision surfaces and
weight vertex groups. We show a series of graphics examples that demonstrate
the quality, predictability and flexibility of our results in a real
production environment with software blender.
\end{abstract}

@@

\copyrightspace

>>>>

%% LyX 2.0.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,review]{acmsiggraph}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amssymb}
\usepackage{graphicx}

@@

% Author and Affiliation (multiple authors).
\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}
\qquad  Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}
 \\Cimalab Research Group\\National University of Colombia}
%\and Ton Roosendaal\thanks{e-mail:ton@blender.org}\\ Blender CEO}

% The ``pdfauthor'' command accepts the authors of the work,
% comma-delimited, and adds this information to the PDF metadata.
%\pdfauthor{Alexander Pinzon, Eduardo Romero, Ton Roosendaal}
\pdfauthor{Anonymous}

@@

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel method for modeling polygonal mesh using
curvature enhancing. This method use our extension of Laplace Beltrami
operator for hybrid quad/triangle meshes to enhance global curvature
in the model. This work present a novel applications of curvature
enhancement in sculpting and modeling with subdivision surfaces and
weight vertex groups. We show a series of graphics examples that demonstrate
the quality, predictability and flexibility of our results.
\end{abstract}

@@

%\copyrightspace
